---
title: 'Tidy Tuesday #2'
author: "Audrey Smyczek"
output: 
  html_document:
    df_print: paged
    code_download: true
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=FALSE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(tidyverse)     # for graphing and data cleaning
library(lubridate)     # for date manipulation
library(ggthemes)      # for even more plotting themes
library(janitor)       # for cleaning variable names
theme_set(theme_minimal()) # My favorite ggplot() theme :)
```


```{r}

illiteracy <- readr::read_csv("https://raw.githubusercontent.com/ajstarks/dubois-data-portraits/master/challenge/2022/challenge06/data.csv")

```


```{r}

white_line <- tibble(Date = c(seq(1860, 1900, 10), seq(1860, 1890, 10), seq(1860, 1880, 10), seq(1860, 1870, 10)), 
                     `Iliteracy Rate` = c(rep(50, 5), rep(67.2, 4), rep(81.6, 3), rep(92.1, 2)))

illiteracy %>% 
  ggplot(aes(x = `Date`, y = `Iliteracy Rate`))+
  geom_bar(stat = "identity", width = 2, fill = "black")+
  geom_line(data = white_line, aes(group = `Iliteracy Rate`), size = 3, color = "#eae3c9")+
  labs(title =  "ILLITERACY.", y = "PERCENT OF\n ILLITERACY.", x = NULL,
       caption = "Plot created by Audrey Smyczek.\n Data from ajstarks via GitHub.")+
    scale_x_continuous(labels = c("1860" = "99%",
                              "1870" = "92.1%",
                              "1880" = "81.6%",
                              "1890" = "67.2%",
                              "1900" = "(50%?)"))+
  scale_y_continuous(breaks = c(99, 92, 81, 67, 50),
                     labels = c("99" = "1860",
                                "92" = "1870",
                                "81" = "1880",
                                "67" = "1890",
                                "50" = "(1900?)"))+
  theme(aspect.ratio = 3/2,
        plot.title = element_text(size = 10,
                                  hjust = 0.5,
                                  face = "bold"),
        plot.caption = element_text(size = 8,
                                    hjust = 0.5),
        plot.background = element_rect(fill = "#d4c7b7"),
        axis.title.y.left = element_text(size = 6,
                                         vjust = 0,
                                         angle = 360,
                                         face = "bold"),
        plot.margin = margin(t = 10,
                             r = 50,
                             b = 10,
                             l = 10),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

```


ALT TEXT: A bar graph of a combination of vertical and horizontal lines with a tan background color, the title of the graph is "Illiteracy". The graph shows are 5 vertical black bars of varying size in descending order from left to right. There are 4 horizontal tan bars that connect the top of the black bar furthest on the right to the black bar on the far left, the lines imitating grid lines. The x-axis of the graph shows the percentage of people who are illiterate, moving from 99 to 92.1 to 81.6 to 67.2 to 50 percent of people. On the y-axis there are years in descending order starting from 1860 to 1900. The graph shows a negative correlation between years and illiteracy, as time moves forward, the number of people who are illiterate decreases. This graph is a replica of the graph created by W.E.B. Dubois for the 1900 Paris Exposition. The plot was created by Audrey Smyczek and the data was from user ajstarks from GitHub.

